Automated discovery \\ of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Specify complexity ranges

% \todo{Specify how combinations of operators are ruled out}

@@

We show the workflow of this work in figure \ref{fig:Gaussian_m1_fit}.
On the leftmost panel, we show the posterior density in primary mass for every event in GWTC3.
In the left-middle panel, we show a GMM fitted to the data given by \cite{Tiwari:2020vym}.
Given the \ppd shown in the middle panel, we use symbolic regression to extract effective descriptions of the data. 
As we increase the complexity of the equation, it is natural to expect that the equation should fit the data better than a lower complexity equation since it has additional free parameters.
At the same time, an equation with higher complexity could either be overfitting or difficult to interpret.
\pysr uses a score (see \citealt{cranmerDiscoveringSymbolicModels2020} for details) as a metric normalized to complexity to show how well an equation is fitting the data.
At each complexity, \pysr outputs the equation with the lowest loss.
To select the equations shown in figure \ref{fig:Gaussian_m1_fit}, we first make an accuracy cut based on the loss of the function, so the selected equation would be a good fit to the data.
Then under a certain loss level, we select the equation that has the highest score.
We choose three accuracy levels to select three different equations in our analysis.
% \todo{Specify how the thresholds were chosen}
The equations selected under these criteria are tabulated in table \ref{tab:equations}.
Note that we take the absolute value of the equations in order to make figure \ref{fig:Gaussian_m1_fit}.

>>>>

@@

We show the workflow of this work in figure \ref{fig:Gaussian_m1_fit}.
On the leftmost panel, we show the posterior density in primary mass for every event in GWTC3.
In the left-middle panel, we show a GMM fitted to the data given by \cite{Tiwari:2020vym}.
Given the \ppd shown in the middle panel, we use symbolic regression to extract effective descriptions of the data. 
As we increase the complexity of the equation, it is natural to expect that the equation should fit the data better than a lower complexity equation since it has additional free parameters.
At the same time, an equation with higher complexity could either be overfitting or difficult to interpret.
\pysr uses a score (see \citealt{cranmerDiscoveringSymbolicModels2020} for details) as a metric normalized to complexity to show how well an equation is fitting the data.
At each complexity, \pysr outputs the equation with the lowest loss.
To select the equations shown in figure \ref{fig:Gaussian_m1_fit}, we first make an accuracy cut based on the loss of the function such that all expressions have a loss lower than $0.3$, so the selected equation would still be a good fit to the data.
We then consider the expressions with the highest score among three ranges: $c\in [1, 20]$,
$c\in[20, 35]$, and $c\in[35, 50]$.
These ranges are set to simply give us a variety of complexity expressions to study.
The equations selected under these criteria are tabulated in table \ref{tab:equations}.
